On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-03-16 MS.tex
Fixed ref: not using abbrev anymore, Fixed comma in equation 3, and in effect sizes

The \textbf{growth rate in height} can likewise be decomposed as the product of several meaningful terms:
\begin{equation}\label{eq:eq2}
\underbrace{\frac{\ud H}{\ud t}}_{\text{growth rate in height}} = \underbrace{\frac{\ud H}{\ud A_{\rm l}}}_{\text{architecture layout}} \times \underbrace{{\frac{\ud A_{\rm l}}{\ud M_{\rm a} }}}_{\text{leaf deployment per mass}} \times {\frac{\ud M_{\rm a} }{\ud B}} \times {\frac{\ud B}{\ud t}},
\end{equation}
where $\ud H / \ud A_{\rm l}$ is the growth in plant height
per unit growth in total leaf area. This term expresses the architectural
strategy of the plant. We assume it is unrelated to the traits considered in the current paper, in other words that it does not automatically change in response to changes in the traits. The term $\ud A_{\rm l} / \ud M_{\rm a} $
accounts for the marginal cost of deploying an additional unit of leaf
area, including construction of the leaf itself and various support
structures.  $\ud A_{\rm l} / \ud M_{\rm a} $
can itself be expressed as a sum of costs per unit leaf
area for constructing various support tissues,
\begin{equation}\label{eq:daldmt}
\frac{\ud A_{\rm l}}{\ud M_{\rm a} }
= \left(\frac{\ud M_{\rm l}}{\ud A_{\rm l}}
 +  \frac{\ud M_{\rm s}}{\ud A_{\rm l}} + \frac{\ud M_{\rm r}}{\ud A_{\rm l}}\right)^{-1}.
\end{equation}

>>>>

The \textbf{growth rate in height} can likewise be decomposed as the product of several meaningful terms:
\begin{equation}\label{eq:eq2}
\underbrace{\frac{\ud H}{\ud t}}_{\text{growth rate in height}} = \underbrace{\frac{\ud H}{\ud A_{\rm l}}}_{\text{architecture layout}} \times \underbrace{{\frac{\ud A_{\rm l}}{\ud M_{\rm a} }}}_{\text{leaf deployment per mass}} \times {\frac{\ud M_{\rm a} }{\ud B}} \times {\frac{\ud B}{\ud t}}
\end{equation}
where $\ud H / \ud A_{\rm l}$ is the growth in plant height
per unit growth in total leaf area. This term expresses the architectural
strategy of the plant. We assume it is unrelated to the traits considered in the current paper, in other words that it does not automatically change in response to changes in the traits. The term $\ud A_{\rm l} / \ud M_{\rm a} $
accounts for the marginal cost of deploying an additional unit of leaf
area, including construction of the leaf itself and various support
structures.  $\ud A_{\rm l} / \ud M_{\rm a} $
can itself be expressed as a sum of costs per unit leaf
area for constructing various support tissues,
\begin{equation}\label{eq:daldmt}
\frac{\ud A_{\rm l}}{\ud M_{\rm a} }
= \left(\frac{\ud M_{\rm l}}{\ud A_{\rm l}}
 +  \frac{\ud M_{\rm s}}{\ud A_{\rm l}} + \frac{\ud M_{\rm r}}{\ud A_{\rm l}}\right)^{-1}.
\end{equation}
